Data Preparation

### 2019-02-15 Data Preparation.Rmd
debug

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID` = `Student Number`,
    `Course ID`  = `Module (Abbrev.)`,
    `Academic Year`,
    Period       = `Academic Session`,
    Grade        = `Grade symbol`
    ) %>%

@@

    time = paste(
      `Academic Year`, substr(Period, 1, 1),
      sep = ""
      ),

    `Academic Year`= paste(
      `Academic Year`, `Academic Year` + 1,
      sep = "-")

>>>>

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical =`Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
    ) %>%

@@

    time = paste(
      Year_numerical, substr(Period, 1, 1),
      sep = ""
      ),

    `Academic Year`= paste(
      Year_numerical, Year_numerical + 1,
      sep = "-")
